A Topic Model of Climate Change Literature

### 2017-09-13 main.tex
Update on Overleaf.

\textbf{
To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}. With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading. We collect over 400,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus. This overview shows us the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports. [We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.]
}

@@

The topic model presented here is a rough map of climate change research since 1985. It shows a broad outline of the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time. This relief map should supplement the maps drawn by assessment-makers-as-cartographers for policymakers described in \citet{Edenhofer2015}, by allowing assessment makers to have an overview of unmanageably large and diverse landscape. Moreover, as demonstrated in this paper, such a map can be used as a reference to quantitatively measure whether the more detailed maps produced, for example, in IPCC reports, accurately reflect the underlying landscape. [map metaphor overworked?]

@@

\begin{figure}
	\includegraphics[width=\linewidth]{plots/wos_scopus_docs_time}
    \caption{Growth in relevant literature in WoS and Scopus}
    \label{growth}
\end{figure}

>>>>

\textbf{
To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}. With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading. We collect over 400,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus. This overview shows us the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports. %[We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.]
}

\begin{figure}
\begin{center}
	\includegraphics[width=0.8\linewidth]{plots/wos_scopus_docs_time}
    \caption{Growth in relevant literature in WoS and Scopus}
    \label{growth}
    \end{center}
\end{figure}

@@

Assessment-makers like the IPCC have been described as cartographers for policymakers \citep{Edenhofer2015}. As such their purpose is, summarising available scientific knowledge, to describe the problem and solution space of a policy issue. The topic model presented here is a rough map of climate change research since 1985. It shows a broad outline of the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time. Such a map sheds light on the terrain of knowledge about a policy issue, making an overview of an unmanageably large and diverse landscape possible. This overview allows both for the production of policy pathways that are well informed by science, and, as demonstrated in this paper, the assessment of the comprehensiveness with which these pathways reflect the landscape.

@@
